Leaf traits drive differences in biomass partitioning among major plant functional types

### 2015-01-07 manuscript.Rnw
minor fix

Next, we decomposed LMF into two components, $LMF = M_F/M_T = M_F/A_S * A_S/MT$, where $M_F/A_S$ is the ratio of leaf biomass to stem basal area (see Methods S2), and $A_S/M_T$ the ratio of stem basal area to total above-ground biomass. We found that the first term showed identical PFT patterns as LMF (Fig 2d and e), $M_F/A_S$ was highly variable between PFT and proportional to LMA, so that $A_F/A_S$ is invariant between PFTs. This decomposition is also convenient because the first term is nearly independent of plant height (Tables 1 and 2), allowing a more straightforward analysis of climate effects (not having to correct for height every time). The second term ($A_S/MT$) was found to be nearly unaffected by PFT, but strongly height-dependent (Fig. S4). It thus absorbs variation related to height and above-ground plant geometry, and is consistent with previous findings that this ratio is fairly conserved between plant species \citep{chave2005}.

>>>>

Next, we decomposed LMF into two components, $LMF = M_F/M_T = M_F/A_S * A_S/M_T$, where $M_F/A_S$ is the ratio of leaf biomass to stem basal area (see Methods S2), and $A_S/M_T$ the ratio of stem basal area to total above-ground biomass. We found that the first term showed identical PFT patterns as LMF (Fig 2d and e), $M_F/A_S$ was highly variable between PFT and proportional to LMA, so that $A_F/A_S$ is invariant between PFTs. This decomposition is also convenient because the first term is nearly independent of plant height (Tables 1 and 2), allowing a more straightforward analysis of climate effects (not having to correct for height every time). The second term ($A_S/MT$) was found to be nearly unaffected by PFT, but strongly height-dependent (Fig. S4). It thus absorbs variation related to height and above-ground plant geometry, and is consistent with previous findings that this ratio is fairly conserved between plant species \citep{chave2005}.
